---
title: "Chapter 8: Introduction to linear regression"
author: "Alexis Mekueko"
date: "10/24/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  slidy_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
header-includes:
- \usepackage{tikz}
- \usetikzlibrary{positioning,shapes.multipart,shapes}
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R Packages

```{r load-packages, message=FALSE}

library(tidyverse) #loading all library needed for this assignment
library(openintro)
#head(fastfood)
library(readxl)
library(data.table)
#library(DT)
library(knitr)

library(readr)
#library(plyr)
library(dplyr)
library(stringr)
#library(XML)
#library(RCurl)
#library(jsonlite)
#library(httr)

#library(maps)
#library(dice)
# #library(VennDiagram)
# #library(help = "dice")
#ibrary(DBI)
#library(dbplyr)

# library(rstudioapi)
# library(RJDBC)
# library(odbc)
# library(RSQLite)
# #library(rvest)

#library(readtext)
#library(ggpubr)
#library(fitdistrplus)
#library(ggplot2)
#library(moments)
#library(qualityTools)
#library(normalp)
#library(utils)
#library(MASS)
#library(qqplotr)
library(DATA606)

```

Github Link: https://github.com/asmozo24/DATA606_Lab6

Web link: https://rpubs.com/amekueko/680865


### Introduction to linear regression


The Human Freedom Index is a report that attempts to summarize the idea of “freedom” through a bunch of different variables for many countries around the globe. It serves as a rough objective measure for the relationships between the different types of freedom - whether it’s political, religious, economical or personal freedom - and other social and economic circumstances. The Human Freedom Index is an annually co-published report by the Cato Institute, the Fraser Institute, and the Liberales Institut at the Friedrich Naumann Foundation for Freedom.

In this lab, you’ll be analyzing data from Human Freedom Index reports from 2008-2016. Your aim will be to summarize a few of the relationships within the data both graphically and numerically in order to find which variables can help tell a story about freedom.


##The data
The data we’re working with is in the openintro package and it’s called hfi, short for Human Freedom Index.

#Exercice 1

What are the dimensions of the dataset?



```{r}

data(hfi)

```

#Exercice 2

What type of plot would you use to display the relationship between the personal freedom score, pf_score, and one of the other numerical variables? Plot this relationship using the variable pf_expression_control as the predictor. Does the relationship look linear? If you knew a country’s pf_expression_control, or its score out of 10, with 0 being the most, of political pressures and controls on media content, would you be comfortable using a linear model to predict the personal freedom score?

```{r, results="asis", echo=FALSE}

#cat(paste0("The most popular article from New York Times shared on facebook: ","[", "[click here]", "](", sampl1, ")","\n"), "\n")
#cat(paste0("The most viewed article on The New York Times: ","[", "[click here]", "](",sampl2, ")","\n"))

```

```{r, results="asis", echo=FALSE}

#cat(paste0("The most popular article from New York Times shared on facebook: ","[", "[click here]", "](", sampl1, ")","\n"), "\n")
#cat(paste0("The most viewed article on The New York Times: ","[", "[click here]", "](",sampl2, ")","\n"))

```

```{r, results="asis", echo=FALSE}

#cat(paste0("The most popular article from New York Times shared on facebook: ","[", "[click here]", "](", sampl1, ")","\n"), "\n")
#cat(paste0("The most viewed article on The New York Times: ","[", "[click here]", "](",sampl2, ")","\n"))

```

```{r, results="asis", echo=FALSE}

#cat(paste0("The most popular article from New York Times shared on facebook: ","[", "[click here]", "](", sampl1, ")","\n"), "\n")
#cat(paste0("The most viewed article on The New York Times: ","[", "[click here]", "](",sampl2, ")","\n"))

```


                   

#Conclusion 
The New York Times API can be easy to use in scraping articles published on their website. However, I think the website it is pretty nested and need a better understanding of the New York Times website structure. 

\tikzset{basic/.style={
        draw,
        rectangle split,
        rectangle split parts=2,
        rectangle split part fill={blue!20,white},
        minimum width=2.5cm,
        text width=2cm,
        align=left,
        font=\itshape
    },
    Diamond/.style={ diamond, 
                        draw, 
                        shape aspect=2, 
                        inner sep = 2pt,
                        text centered,
                        fill=blue!10!white,
                        font=\itshape
                      }
        }


